\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-11-24 icra-2021.tex
fixed that proof finally (now I can forget it I hope...)

\begin{lem}[Representations equivalence]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zero) and the control is zero. Suppose further matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is $\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}$. Then Equation~(\ref{eq:fourier}) describes the same signal as Equation~(\ref{eq:state-perf}).
\end{lem}

The equivalence of the models is trivial and the coefficients are chosen such that the two Equations produce the same expression. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof.

@@

This appendix is a formal proof of Lemma~\ref{lem:eqv}.

The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ such that the coefficients $a_0,\dots,b_r$ are the same as the coefficients $\alpha_0,\dots,\beta_r$.

We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$. With $t=\omega jt$, we find the expression for $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively. This leads~\cite{kuo1967automatic}
\begin{equation}\begin{split}\label{eq:proof-complex}
  h(t)=a_0/T+&(1/T)\sum_{j=1}^{r}{e^{i\omega jt}(a_j-ib_j)}+\\&(1/T)\sum_{j=1}^{r}{e^{-i\omega jt}(a_j+ib_j)},
 \end{split}\end{equation}
where $i$ is the imaginary unit.

The solution at time $t$ can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$. Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbooks~\cite{kuo1967automatic, ogata2002modern}. To solve the matrix exponential $e^{At}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.

The method works on the similarity transformation $A_c=VDV^{-1}$. The power series definition of $e^{At}$ implies $e^{At}=Ve^{Dt}V^{-1}$~\cite{moler2003nineteen}. We consider the non-singular matrix $V$, whose columns are eigenvectors of $A$; $V:=\begin{bmatrix}v_0 & v_1^0 & v_1^1 & \dots & v_r^0 & v_r^1\end{bmatrix}$. We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$. $\lambda_0$ is the eigenvalue associated to the first item of $A$. $\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j$. We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.

We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions; $\dot{\mathbf{q}}=A\mathbf{q}$. Initial guess is expressed as a combination of eigenvectors $\mathbf{q}_0=\mathbf{\gamma}V$. The generic solution is $\mathbf{q}=\mathbf{\gamma}e^{Dt}V$. % to rewrite this so it's exactly as in the proof

Let us consider the linear combination of all the coefficients of the state at time $t$. This can be expressed in the following form
\begin{equation}\label{eq:proof-output}\begin{split}
  \gamma_0e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^1t}v_j^1},
\end{split}\end{equation}
we proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}). % the V and gamma are wrong sizes. You put zeros so you fill them (look at the sheet where you sketched it before)

@@

We proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches. We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$. The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=0\,\,\,\forall v_0$, thus we choose $v_0=1$. We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $a_0=\gamma_0$.

@@

For the first block $A_1$, we find the eigenvalues from $\det(A_1-\lambda I)=0$. The polynomial $\lambda^2+\omega^2$, gives two complex roots--the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$. The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}-i&1\end{bmatrix}^T$. The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}i&1\end{bmatrix}^T$. Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega t}(a_1-ib_1)=\gamma_1e^{i\omega t}\begin{bmatrix}-i&1\end{bmatrix}^T$ and $e^{-i\omega t}(a_1+ib_1)=\gamma_1e^{i\omega t}\begin{bmatrix}i&1\end{bmatrix}^T$ hold. They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.

The proof for the remaining $r-1$ blocks is equivalent.

We thus conclude that the lemma holds.

@@

If there are any following stages in the survey, they are constructed the same way. Th stages $\mathcal{M}_i$ for $i:=\{0,4,8,\dots\}$ contain TEE circle with variable radius. For $i:=\{1,3,5,\dots\}$ TEE line with variable displacement. For $i:=\{2,6,10,\dots\}$ TEE circle with fixed radius and variable displacement.

>>>>

\begin{lem}[Signals equality]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zero) and the control is zero. Suppose further matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is $\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}$. Then Equation~(\ref{eq:fourier}) describes the same signal as Equation~(\ref{eq:state-perf}).
\end{lem}
\begin{proof}
The equivalence of the models is trivial and the coefficients are chosen such that the two Equations produce the same expression. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof.
\end{proof}

@@

We propose a formal proof of Lemma~\ref{lem:eqv}. The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ in Equation~(\ref{eq:state-details}). We write these elements such that the coefficients of the series $a_0,\dots,b_r$ are the same as the coefficients of the state $\alpha_0,\dots,\beta_r$.

Let us re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$. With $t=\omega jt$, we find the expression for $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively. This leads~\cite{kuo1967automatic}
\begin{equation}\begin{split}\label{eq:proof-complex}
  h(t)=a_0/T+&(1/T)\sum_{j=1}^{r}{e^{i\omega jt}(a_j-ib_j)}+\\&(1/T)\sum_{j=1}^{r}{e^{-i\omega jt}(a_j+ib_j)},
 \end{split}\end{equation}
where $i$ is the imaginary unit.

The solution at time $t$ can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$. Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using standard textbooks~\cite{kuo1967automatic, ogata2002modern}. To solve the matrix exponential $e^{At}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.

The method works on the similarity transformation $A=VDV^{-1}$. The power series definition of $e^{At}$ implies $e^{At}=Ve^{Dt}V^{-1}$~\cite{moler2003nineteen}. We consider the non-singular matrix $V$, whose columns are eigenvectors of $A$; $V:=\begin{bmatrix}v_0 & v_1^0 & v_1^1 & \dots & v_r^0 & v_r^1\end{bmatrix}$. We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$. $\lambda_0$ is the eigenvalue associated to the first item of $A$. $\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j$. We can write $Av_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.

We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions; $\dot{\mathbf{q}}=A\mathbf{q}$. The linear combination of the initial guess and the generic solution
\begin{equation*}\begin{split}
  F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}}\\
  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}}
\end{split}\end{equation*}
where $F=\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ is a properly sized vector of ones.

Let us consider the second expression. It represents the linear combination of all the coefficients of the state at time $t$. It can also be expressed in the following form
\begin{equation}\label{eq:proof-output}\begin{split}
  \gamma_0 e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
\end{split}\end{equation}

We proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).

@@

We proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches. We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$. The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=\begin{bmatrix} 0 & \cdots & 0 \end{bmatrix}\,\,\,\forall v_0$, thus we choose $v_0=\begin{bmatrix}1 & 0 & \cdots & 0\end{bmatrix}$. We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $\gamma_0=\begin{bmatrix}a_0 & 0 & \cdots & 0\end{bmatrix}$.

@@

For the first block $A_1$, we find the eigenvalues from $\det(A_1-\lambda I)=0$. The polynomial $\lambda^2+\omega^2$, gives two complex roots--the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$. The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}0 & -i&1&0&\cdots&0\end{bmatrix}^T$. The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}0&i&1&0&\cdots&0\end{bmatrix}^T$. Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega t}(a_1-ib_1)=\gamma_1 e^{i\omega t}v_1^0$ and $e^{-i\omega t}(a_1+ib_1)=\gamma_1 e^{i\omega t}v_1^1$ hold. They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$. The proof for the remaining $r-1$ blocks is equivalent.

The initial guess is build such that the sum of the coefficients is the same in both the signals. The output matrix is built as follows. The coefficient $1/T$ accounts for the period in Equations~(\ref{eq:proof-complex}--\ref{eq:proof-output}) and~(\ref{eq:fourier}). At time instant zero, the coefficients $b_j$ are not present (and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$). Thus to match the outputs $h(t)=y(t)$ we define $C=1/T\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$. We thus conclude that the lemma holds.

We note that the signal would still be periodic with another linear combination of coefficients (for instance, $C=\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$). Even if both the signals $h$ and $y$ would be still periodic, they would not be equal.

@@

If there are any following stages in the survey, they are constructed the same way. The stages $\mathcal{M}_i$ for $i:=\{0,4,8,\dots\}$ contain TEE circle with variable radius. For $i:=\{1,3,5,\dots\}$ TEE line with variable displacement. For $i:=\{2,6,10,\dots\}$ TEE circle with fixed radius and variable displacement.
